A Switching Planner for Combined Task and Observation Planning

### 2011-04-21 subarchitectures/planner.sa/trunk/src/latex/AAAI11/prop-dtp.tex
Got rid of one of the paragraph

%% {\em runtime variables}
%% {\em decision variables}
%% {\em uninitialised variables}
%% {\em omitted variables}

@@

%% We model a process state $\state$ as the set of propositions that are
%% true of the state. Notationally, we have $\state \subseteq
%% \props$. State change is induced by application of actions. A
%% stochastic action $\stochAction \in \stochActions$ is applicable if
%% its precondition $\poss(\stochAction)$, a set of propositions, are
%% satisfied in the current state. We write $\stochActions(\state)$ for set of actions
%% applicable at state $\state$.  If action $\stochAction \in
%% \stochActions(\state)$ is applied at \state, nature chooses one
%% element amongst a small set of deterministic outcomes
%% $\detActions(\stochAction) \equiv \{\detAction_1, \ldots, \detAction_k
%% \}$. We denote $\mu_{\stochAction}(\detAction_i)$ the probability that
%% nature takes outcome $\detAct_i$, and for all \stochAction\ we require
%% $\sum_{\detAction_i \in \detActions(\stochAction)}
%% \mu_{\stochAction}(\detAction_i) = 1$. The chosen outcome has an
%% effect on the state given in terms of two lists of propositions. The
%% add-list $\add(\detAction)$ and delete-list
%% $\delete(\detAction)$.\footnote{If a proposition is in the add-list of
%% $\detAction$, then it cannot be in the delete-list and vice versa.}
%% If outcome $\detAction$ with $\add(\detAction) := [\prop_1,
%% ..,\prop_n]$ and $\delete(\detAction) := [\prop_{n+1},
%% ..,\prop_m]$ is chosen by nature when \stochAction\ is
%% applied at state $\state$, then the resultant state is $ ( \state \cup
%% \add(\detAction) ) \backslash \delete(\detAction)$ -- i.e.,
%% propositions from $\add(\detAction)$ are added to $\state$, and those
%% from $\delete(\detAction)$ are removed from $\state$.

%% \citeauthor{rintanen:01}~(\citeyear{rintanen:01})

@@

Finally, we make some fairly standard assumptions. First, that action
execution and sensing occur instantaneously, and that only one action
can be applied per plan-step. Secondly, it can arise that in some
states an action is applicable, and in others it is not. Moreover, a
belief-state can assign non-zero probability to states where that
applicability holds, and states where it does not. %% We differ
%% from~\citeauthor{younes:littman:04}~(\citeyear{younes:littman:04})
%% In beliefs where an action exists that is applicable in some state 
%% with non-zero probability, and not applicable in another, we differ
%% from~\citeauthor{younes:littman:04}~(\citeyear{younes:littman:04}),
%% because 
%% in that
%% we forbid the execution of the action.
%% actions that are not applicable in
%% any state of the current belief.  
%% Also,
Unlike~\citeauthor{hoffmann:brafman:2006}~(\citeyear{hoffmann:brafman:2006}),
we incorporate a PPDDL-like default semantics, treating an action
\stochAction\ executed at $\state_i$ as if it has no effect at
states $\state$ if $\poss(\stochAction) \not\subseteq
\state$.

>>>>

@@

@@

%% Finally, we make some fairly standard assumptions. First, that action
%% execution and sensing occur instantaneously, and that only one action
%% can be applied per plan-step. Secondly, it can arise that in some
%% states an action is applicable, and in others it is not. Moreover, a
%% belief-state can assign non-zero probability to states where that
%% applicability holds, and states where it does not. %% We differ
%% %% from~\citeauthor{younes:littman:04}~(\citeyear{younes:littman:04})
%% %% In beliefs where an action exists that is applicable in some state 
%% %% with non-zero probability, and not applicable in another, we differ
%% %% from~\citeauthor{younes:littman:04}~(\citeyear{younes:littman:04}),
%% %% because 
%% %% in that
%% %% we forbid the execution of the action.
%% %% actions that are not applicable in
%% %% any state of the current belief.  
%% %% Also,
%% Unlike~\citeauthor{hoffmann:brafman:2006}~(\citeyear{hoffmann:brafman:2006}),
%% we incorporate a PPDDL-like default semantics, treating an action
%% \stochAction\ executed at $\state_i$ as if it has no effect at
%% states $\state$ if $\poss(\stochAction) \not\subseteq
%% \state$.
